---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# templates

An R package for Rmarkdown templates. Currently includes:

* SOE template (not 508 Compliant)
* SOE template (508 Compliant) *in progress*
* ... 

## Installation

To install the package, run:

```{r}
remotes::install_github("NOAA-EDAB/templates")
```


## Example

To create a new State of the Ecosystem template, simply:
```{r example, eval = FALSE}
library(templates)
rmarkdown::draft(file = "soe_report.Rmd",
                 template = "soe", 
                 package = "templates")

```

or, after installing the package, click on `create new Rmarkdown document` in Rstudio
to have access to the templates. 

See [Templates for Rmarkdown](http://rmarkdown.rstudio.com/developer_document_templates.html) for more information.

---

